Adaptive Disk Storage for Interaction Graphs

### 2014-07-16 docs/graph-adapt/main.tex
mixed integer linear program updates
Removed my ill-formatted notes
made a minor change to the overhead formuation
changed how overhead constaints are handled

The storage overhead can be formalized as:
\begin{equation}
H(\mathcal{P}, B) = |\mathcal{P}(B)|\cdot\left(1-\frac{c_e(B)\cdot \sum_{a\in A} s(a)}{s(B)}\right) 
\end{equation}

@@

\subsection{Mixed Integer Linear Program Formulation}
$x_{a,p}$: $1$ if attribute $a$ is in partition $p$, $0$ otherwise.\\
$y_{p,q}$: $1$ if partition $p$ is used by query $q$, $0$ otherwise.\\
$z_{a,p,q}$: $1$ if partition $p$ is used by query $q$, and attribute $a$ is in partition $p$, $0$ otherwise.\\
$u_{p}$: $1$ if partition $p$ is assigned at least $1$ attribute, $0$ otherwise.\\
The formulation for ($k$ partitions):

% NOTE: In the simulation we will have query weights that will factor into the objective function
\begin{eqnarray}
\text{minimize} 
    \Big(\sum_{q\in Q} \sum_{p=1}^{k} (16\cdot c_e(B) &+& 12\cdot c_n(B))\cdot y_{p,q}\nonumber\\
    + \sum_{a\in A} s(a)\cdot c_e(B)\cdot z_{a,p,q}\Big) &-& \Big(K \sum_{p=1}^{k} u_p + \sum_{q\in Q} y_{p,q}\Big) \nonumber\\
\text{subject to}\hspace{2.75cm}&&\nonumber\\
\forall_{a\in A}, 
    && \sum_{p=1}^{k} x_{a,p} = 1\nonumber\\
\forall_{\{p,q\}\in [1..k]\times Q}, 
    &&  \sum_{a\in A} q(a)\cdot x_{a,p} - y_{p,q} \geq 0 \nonumber\\
\forall_{\{a,p,q\}\in A\times [1..k]\times Q},
  && z_{a,p,q} - (x_{a,p} + y_{p,q}) \geq -1\nonumber\\
\forall_{p\in[1..k]},
   && \sum_{a\in A} y_{a,p} - u_p \geq 0 \nonumber\\
\Big(1-\frac{c_e(B)\cdot \sum_{a\in A} s(a)}{s(B)}\Big) && \sum_{p=1}^{k} u_p < \alpha \nonumber
\end{eqnarray}

>>>>

The storage overhead can be formalized as:
\begin{equation}
H(\mathcal{P}, B) = (|\mathcal{P}(B)|-1)\cdot\left(1-\frac{c_e(B)\cdot \sum_{a\in A} s(a)}{s(B)}\right) 
\end{equation}

@@

\subsection{Mixed Integer Linear Program Formulation}
$x_{a,p}$: $1$ if attribute $a$ is in partition $p$, $0$ otherwise.\\
$y_{p,q}$: $1$ if partition $p$ is used by query $q$, $0$ otherwise.\\
$z_{a,p,q}$: $1$ if partition $p$ is used by query $q$, and attribute $a$ is in partition $p$, $0$ otherwise.\\

Let $q(a)\equiv \mathbf{1}(a \in q.A)$.

% NOTE: In the simulation we will have query weights that will factor into the objective function
\begin{eqnarray}
\text{minimize} 
    \Big(\sum_{q\in Q} \sum_{p=1}^{k} (16\cdot c_e(B) &+& 12\cdot c_n(B))\cdot y_{p,q}\nonumber\\
    + \sum_{a\in A} s(a)\cdot c_e(B)\cdot z_{a,p,q}\Big) &-& \Big(K\cdot \sum_{p=1}^{k} u_p + \sum_{q\in Q} y_{p,q}\Big) \nonumber\\
\text{subject to}\hspace{2.75cm}&&\nonumber\\
\forall_{a\in A}, 
    && \sum_{p=1}^{k} x_{a,p} = 1\nonumber\\
\forall_{\{p,q\}\in [1..k]\times Q}, 
    &&  \sum_{a\in A} q(a)\cdot x_{a,p} - y_{p,q} \geq 0 \nonumber\\
\forall_{\{a,p,q\}\in A\times [1..k]\times Q},
  && z_{a,p,q} - (x_{a,p} + y_{p,q}) \geq -1\nonumber\\
\end{eqnarray}

We will start with $k=|A|$ and check if the number of partitions used results
on the overhead constraint being satisified, that is:
$$\Big(1-\frac{c_e(B)\cdot \sum_{a\in A} s(a)}{s(B)}\Big) \cdot \Big(\sum_{p=1}^{k} u_p -1\Big) < \alpha$$

If the constraint is satisfied, then we are done. Otherwise, we set
$k=\sum_{p=1}^{k} u_p -1$ and repeat.
